Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-05-08 ICML-camera-ready/appendix-proofs-of-polynomial-approximation-theorems.tex
pushed the scaling into the proof of Theorem 8

\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation}

@@

\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
\end{enumerate}
\end{lemma}

@@

To prove part 3, we use generalized triangle inequality and
\autoref{lemma:simple-inequality}. We have
\[
\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
\]
\end{proof}

@@

We prove the following lemma in this section.
\autoref{theorem:polynomial-approximation-2} immediately
follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
and algebra.

\begin{lemma}
\label{lemma:polynomial-approximation-2}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
Define
$$
r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
$$
Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,

\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,

\item $\deg(p) \le (2s+1) rm$,
\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
\end{enumerate}
\end{lemma}

We define several univariate polynomials
\begin{align*}
P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2, \quad \text{for $n \ge 0$,} \\
A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$,} \\
B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$.}
\end{align*}
We define the polynomial $p:\R^d \to \R$ as
\[
p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
\]

For convenience we define univariate rational function
\begin{align*}
S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)}, \quad \text{for $n,k \ge 0$,}
\end{align*}
and a multivariate rational function
$$
Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
$$
It is easy to verify that
$$
p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
$$

@@

To prove parts 1 and 2 of \autoref{lemma:polynomial-approximation-2} first
note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
Consider any $x$ in either
$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
or in
$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
are the same, it remains to show that $|p(x)| \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$.
Indeed,
\begin{align*}
|p(x)|
& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} \\
& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} \quad \text{(\autoref{lemma:properties-of-q})} \; .
\end{align*}
where we used that $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-\frac 1 4} \ge 1/2$.

@@

To prove part 3 of \autoref{lemma:polynomial-approximation-2} note that
$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.

It remains to prove part 4 of \autoref{lemma:polynomial-approximation-2}.
For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
define multivariate polynomials
\begin{align*}
f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
\end{align*}
Note that
\[
p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
\]
We bound the norms of these polynomials. We have
$$
\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^{2s} \; .
$$
where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}}{\gamma})\right)^2$,
using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
as
\begin{align*}
\norm{q_v}^2
& \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \\
& \le  (2s+1)^{2s+1} (2 \cdot 2^{2s})^{2s + 1} \; .
\end{align*}
Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
\begin{align*}
\norm{a_v}^2
& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
& \le 2 r^{r(2s+1)} (\norm{q_v}^{2})^r + 2 r^{r(2s+1)} (\norm{q_{-v}}^{2})^r \\
& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{r} \\
& = 4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \; .
\end{align*}
The same upper bound holds for $\norm{b_v}^2$. Finally,
\begin{align*}
\norm{p} 
& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] \\
& \qquad + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \right)^{m/2} \\
& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2) \right)^{(s+1/2)rm} \; .
\end{align*}

>>>>

\section{Proofs of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation}

@@

\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
$\norm{\sum_{j=1}^n p_j} \le \sum_{j=1}^n \norm{p_j}$.
Consequently,
$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
\end{enumerate}
\end{lemma}

@@

The first inequality of part 3 follows from triangle inequality in Euclidean spaces, by viewing the polynomials
$p = \sum_{A} c_A x^A$ as multidimensional vectors $(c_A)$, and $\| p \| = \| (c_A) \|$.

For the second inequality, by~\autoref{lemma:simple-inequality}, we have
\[
\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
\]
\end{proof}

@@

%We prove the following lemma in this section.
%\autoref{theorem:polynomial-approximation-2} immediately
%follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
%and algebra.

%\begin{lemma}
%\label{lemma:polynomial-approximation-2}
%Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
%\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
%Define
%$$
%r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
%$$
%Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
%\begin{enumerate}
%\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,

%\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,

%\item $\deg(p) \le (2s+1) rm$,
%\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
%\end{enumerate}
%\end{lemma}

We define several univariate polynomials
\begin{align*}
P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2, \quad \text{for $n \ge 0$,} \\
A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$,} \\
B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$.}
\end{align*}
We define the polynomial $p':\R^d \to \R$ as
\[
p'(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
\]
Finally, we define the polynomial $p := 2^{-s(s+1)rm+1} \cdot p'$. We are going to show
that this polynomial $p$ satisfies the required properties.

For convenience we define univariate rational function
\begin{align*}
S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)}, \quad \text{for $n,k \ge 0$,}
\end{align*}
and a multivariate rational function
$$
Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
$$
It is easy to verify that
$$
p'(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
$$

@@

To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
Consider any $x$ in either
$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
or in
$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
are the same, it remains to show that $|p(x)| \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$.
Indeed,
\begin{align*}
|p(x)|
& = 2^{-s(s+1)rm+1} \cdot |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
& \ge 2^{-s(s+1)rm+1} \cdot |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
& \ge |Q(x)| \ge \frac{1}{2} \quad \text{(\autoref{lemma:properties-of-q})} \; .
\end{align*}
where we used that $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-\frac 1 4} \ge 1/2$.

@@

To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.

It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
define multivariate polynomials
\begin{align*}
f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
\end{align*}
Note that
\[
p'(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
\]
We bound the norms of these polynomials. We have
$$
\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^{2s} \; .
$$
where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}}{\gamma})\right)^2$,
using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
as
\begin{align*}
\norm{q_v}^2
& \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \\
& \le  (2s+1)^{2s+1} (2 \cdot 2^{2s})^{2s + 1} \; .
\end{align*}
Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
\begin{align*}
\norm{a_v}^2
& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
& \le 2 r^{r(2s+1)} (\norm{q_v}^{2})^r + 2 r^{r(2s+1)} (\norm{q_{-v}}^{2})^r \\
& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{r} \\
& = 4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \; .
\end{align*}
The same upper bound holds for $\norm{b_v}^2$. Therefore,
\begin{align*}
\norm{p'}
& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] \\
& \qquad + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \right)^{m/2} \\
& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2) \right)^{(s+1/2)rm} \; .
\end{align*}
Finally,
$\norm{p} = 2^{-s(s+1)rm+1} \norm{p'} \leq (4m-1) 2^m \cdot \left(2^s rm (4s+2) \right)^{(s+1/2)rm}$. The theorem follows.

### 2019-05-08 ICML-camera-ready/from-weak-separability-to-strong-separability.tex
some formatting issue
pushed the scaling into the proof of Theorem 8

This corollary follows directly from
Theorems~\ref{theorem:kernelized-upper-bound}
and~\ref{theorem:margin-transformation}.

>>>>

This corollary follows directly from
Theorems~\ref{theorem:kernelized-upper-bound}
and~\ref{theorem:margin-transformation}. We remark that under the weakly linearly
separable setting,~\citep{Daniely-Helbertal-2013} gives a mistake lower bound of
$\Omega(\frac{K}{\gamma^2})$ for {\em any algorithm} (see also~\autoref{theorem:strongly-separable-examples-mistake-lower-bound}).
We leave the possibility of designing efficient algorithms that
have mistakes bounds matching this lower bound as an important open question.

### 2019-05-08 ICML-camera-ready/introduction.tex
pushed the scaling into the proof of Theorem 8

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being time and memory efficient.~\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

>>>>

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being time and memory efficient.\footnote{We call an algorithm
 computationally efficient, if its running time is polynomial in $K$, $d$, $1/\gamma$
 and $T$.}
\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

### 2019-05-08 ICML-camera-ready/title-and-abstract.tex
add camera-ready folder
entomological changes; reviews; some formatting issues fixed
pushed the scaling into the proof of Theorem 8

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}

@@

\begin{icmlauthorlist}
\icmlauthor{Alina Beygelzimer}{yahoo}
\icmlauthor{D\'avid P\'al}{yahoo}
\icmlauthor{Bal\'azs Sz\"or\'enyi}{yahoo}
\icmlauthor{Devanathan Thiruvenkatachari}{nyu}
\icmlauthor{Chen-Yu Wei}{usc}
\icmlauthor{Chicheng Zhang}{microsoft}

@@

\icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
\icmlaffiliation{nyu}{New York University, New York, MA, USA}
\icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
\icmlaffiliation{microsoft}{Microsoft Research, New York, NY, USA}

@@

@@

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
Our algorithm
is based on kernel Perceptron, which is inspired by the work
of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
%is based on a infinite-dimensional feature mapping that transforms weakly linear
%separable examples to strongly linear separable examples, which in turn is
%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
\end{enumerate}
\end{abstract}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
%\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}

%\twocolumn[
%\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}

\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}

@@

\begin{icmlauthorlist}
\icmlauthor{D\'avid P\'al}{yahoo}
\icmlauthor{Bal\'azs Sz\"or\'enyi}{yahoo}
\icmlauthor{Devanathan Thiruvenkatachari}{nyu}
\icmlauthor{Chen-Yu Wei}{usc}
\icmlauthor{Chicheng Zhang}{microsoft}
\icmlauthor{Alina Beygelzimer}{yahoo}

@@

\icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
\icmlaffiliation{nyu}{New York University, New York, NY, USA}
\icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
\icmlaffiliation{microsoft}{Microsoft Research, New York, NY, USA}

@@

%\title{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}

%\begin{icmlauthorlist}
%\author[1]{Alina Beygelzimer \thanks{beygel@verizonmedia.com}}
%\author[1]{D\'avid P\'al \thanks{dpal@verizonmedia.com}}
%\author[1]{Bal\'azs Sz\"or\'enyi \thanks{balazs.szorenyi@verizonmedia.com}}
%\author[2]{Devanathan Thiruvenkatachari\thanks{dt1295@nyu.edu}}
%\author[3]{Chen-Yu Wei\thanks{chenyu.wei@usc.edu}}
%\author[4]{Chicheng Zhang\thanks{chicheng.zhang@microsoft.com}}

%beygel@oath.com
%balazs.szorenyi@oath.com
%szorenyi.balazs@gmail.com
%beygel@gmail.com
%davidko.pal@gmail.com
%\end{icmlauthorlist}

%\affil[1]{Yahoo Research, New York, NY, USA}
%\affil[2]{New York University, New York, MA, USA}
%\affil[3]{University of Southern California, Los Angeles, CA, USA}
%\affil[4]{Microsoft Research, New York, NY, USA}

%\maketitle
%\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}

%\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}

%\vskip 0.3in
%]

%\printAffiliationsAndNotice{}

@@

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$.\footnote{We use the notation
$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}
Our algorithm
is based on kernel Perceptron, which is inspired by the work
of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
%is based on a infinite-dimensional feature mapping that transforms weakly linear
%separable examples to strongly linear separable examples, which in turn is
%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
\end{enumerate}
\end{abstract}
